First Exclusive Measurement of Deep Virtual Compton Scattering off $^4$He: Toward the 3D tomography of nuclei

### 2017-02-10 eg6-letters/coherent/dvcs_he4_prl.tex
nathans 2nd suggestions

The main background in the measurement of DVCS is coherent $\pi^{0}$ 
production. Therefore, we remove events where a $\pi^{0}$ can be identified by 
invariant mass reconstruction of two photons.  To ensure the interaction 
occurs at the partonic level and the DVCS handbag diagram is dominant, we 
select events with $Q^{2}>1~[GeV^{2}/c^{2}]$. The exclusivity of the events is 
obtained by applying a set of cuts on the following kinematic variables: the 
co-planarity angle ($\Delta \phi$), the missing energy, the missing mass 
squared, the missing transverse momentum, the missing mass squared of the 
$e'^4He'$ system, and the angle ($\theta$) between the measured photon and the 
missing momentum of the $e'^4He'$ system. The most relevant of these cuts are 
presented in Figure~\ref{fig:kin-cuts}, which shows 3$\sigma$ cuts except for the 
missing energy (which appears to be too large and for which we reduced the cut 
window to [-0.45,0.5] GeV). After these requirements, we have about 3200 events 
left, and Figure \ref{fig:kin-coverage} presents their
kinematic distributions in ($Q^{2}$,$x_{B}$) and ($Q^{2}$,$-t$).

@@

We identified two main backgrounds to our measurement, accidental 
coincidences and exclusive $\pi^0$ production. The accidental events have 
particles coming from different events, and we estimate their  contribution
to be 4.1\% of our sample. We evaluated this contribution by selecting events 
passing all our cuts but with an electron and an helium originating from different 
vertices. Regarding the $\pi^0$ production, it can easily be mistaken for DVCS when 
one of the two photons of the $\pi^0$ decay is produced at low energy in the 
laboratory frame and remains undetected. To estimate the importance of this 
background, we developed an event generator calibrated on the experimental yield 
of exclusive $\pi^0$ measured by our experiment. We used this generator together 
with a GEANT3 simulation of our detection system to estimate the ratio between
the number of $\pi^0$ events where the two photons are detected and those that 
would be mistaken for DVCS. This ratio is then multiplied by the measured yield 
of exclusive $\pi^0$ events to correct the DVCS data. Depending on the kinematics, we
found contaminations of 2 to 4\%. The study of systematics errors showed that the main 
contributions come from the choice of the DVCS exclusivity cuts (8\%) and the 
large binning size (5.1\%) [Is that right to add it here?]. However, added quadratically, these 
errors sum up to about 10\%, which always remain significantly smaller than the 
statistical errors.

@@

\begin{figure}[tb]
\includegraphics[width=8.9cm]{figs/coherent-ALU_90.pdf}
\caption{The $Q^{2}$ (left), $x_{B}$ (middle), and $-t$-dependencies (right) of
   the $A_{LU}$ at $\phi$~=~90$^{\circ}$ (black squares). On the 
   middle plot: the full-red and the dashed-blue curves are theoretical 
   calculations from \cite{simonetta_2}. On the right: the green circles are 
   the HERMES $-A_{LU}$ (positron beam was used) inclusive measurements 
   \cite{HERMES_BSA}, the colored curves represent theoretical calculations 
   from \cite{simonetta_2}.}
\label{fig:alu90}
\end{figure}

>>>>

%The main background in the measurement of DVCS is coherent $\pi^{0}$ 
%production. Therefore, we remove events where a $\pi^{0}$ can be identified by 
%invariant mass reconstruction of two photons.

To ensure the interaction 
occurs at the partonic level and the DVCS handbag diagram is dominant, we 
select events with $Q^{2}>1~[GeV^{2}/c^{2}]$. Exclusivity of the coherent DVCS reaction is 
optimized by applying a set of cuts on the following kinematic variables: the 
co-planarity angle ($\Delta \phi$), the missing energy, the missing mass 
squared, the missing transverse momentum, the missing mass squared of the 
$e'^4He'$ system, and the angle ($\theta$) between the measured photon and the 
missing momentum of the $e'^4He'$ system. The most relevant of these cuts are 
presented in Figure~\ref{fig:kin-cuts}, which shows 3$\sigma$ cuts except for the 
missing energy (which appears to be too large and for which we reduced the cut 
window to [-0.45,0.5] GeV).  We also reject events where a $\pi^0$ is identified
by invariant mass reconstruction of two photons.  After these requirements, we have
about 3200 events left, and Figure \ref{fig:kin-coverage} presents their kinematic
distributions in ($Q^{2}$,$x_{B}$) and ($Q^{2}$,$-t$).

@@

We identified two main backgrounds to our measurement, accidental 
coincidences and exclusive, coherent $\pi^0$ production. The accidentals have 
particles originating from different events, and we estimate their  contribution
to be 4.1\% of our sample. We evaluated this contribution by selecting events 
passing all our cuts but with an electron and helium originating from different 
vertices. Regarding the $\pi^0$ production, it can easily be mistaken for DVCS when 
one of the two photons from the $\pi^0$ decay is produced at low energy in the 
laboratory frame and remains undetected. To estimate the importance of this 
background, we developed an event generator calibrated on the experimental yield 
of exclusive $\pi^0$ measured by our experiment. We used this generator together 
with a GEANT3 simulation of our detection system to estimate the ratio between
the number of $\pi^0$ events where the two photons are detected and those that 
would be mistaken for DVCS. This ratio is then multiplied by the measured yield 
of exclusive $\pi^0$ events to correct the DVCS data. Depending on the kinematics, we
found contaminations of 2 to 4\%. The study of systematics errors showed that the main 
contributions come from the choice of the DVCS exclusivity cuts (8\%) and the 
large binning size (5.1\%) [Is that right to add it here?]. However, added quadratically, these 
errors sum up to about 10\%, which always remain significantly smaller than the 
statistical errors.

@@

\begin{figure}[tb]
\includegraphics[width=8.9cm]{figs/coherent-ALU_90.pdf}
\caption{The $Q^{2}$ (left), $x_{B}$ (middle), and $-t$-dependencies (right) of
   the $A_{LU}$ at $\phi$~=~90$^{\circ}$ (black squares). On the 
   middle plot: the full-red and the dashed-blue curves are theoretical 
   calculations from \cite{simonetta_2}. On the right: the green circles are 
   the HERMES $-A_{LU}$ (positron beam was used) inclusive measurements 
   \cite{Airapetian}, the colored curves represent theoretical calculations 
   %\cite{HERMES_BSA}, the colored curves represent theoretical calculations 
   from \cite{simonetta_2}.}
\label{fig:alu90}
\end{figure}
